---
title: "Research"
author: "Patrick Harris"
date: "May 17, 2019"
output:
  html_document: default
  pdf_document: default
---

## Installs needed packages
```{r}
if (!require("rtweet")) {
  install.packages("rtweet")
  library("rtweet")
}
```

## Connects to Twitter 
```{r}
api_key <- api_key
api_secret <- api_secret
token <- token
token_secret <- token_secret
oauth <- create_token(consumer_key = api_key, consumer_secret = api_secret, access_token = token, access_secret = token_secret )
```

## The function that reads the screen names from the console 
```{r}
readname <- function()
{ 
  n <- as.integer(readline(prompt = "Enter the number of Users:  "))
  screenName <- vector(mode = "character", n)
   for(i in 1:n){
     screenName[i] <- readline(prompt = "enter the screen name without spaces before or after: ")
   }

  return(screenName)
}

```


## Utilizes the function that reads the screen names from the console (may need to expand console)
```{r}
names <- (readname())
```
```
## gets information on the followers
```{r}

## an Empty list for the twitter follower IDs
user_complete <- list()

## loops for each 
for (i in 1:length(names)){

  ## gets the follower IDs of name[i]
  user <- get_followers(names[i], n = 150)
  user$University <- names[i]
  
  ## gets information on the followers
  user_info <- lookup_users(user$user_id)
  user_info$University <- names[i]
  
  ## cleans data
  user_info <- subset(user_info, select=c("location", "University", "screen_name"))
  user_info<-subset(user_info, location!="")
  
  ## ads follower information (dataframe) to user_complete (list)
  user_complete[[i]] <- user_info

}
```


## Writes CSV files titled from the screename entered above (screenname_followers.csv)
```{r}
lapply(1:length(user_complete), function(i) write.csv(user_complete[[i]], 
                                      file = paste(names[i], sep ="", "_followers.csv")))
```



